R for Clinical Study Reports and Submission

### 2022-09-20 slides/fda-workshop-slides.Rmd
Deploying to gh-pages from @ elong0527/r4csr@9eb966545461ba0193ea2284e5d1e59f0739f74a 🚀

- During the workshop, we will use `esubdemo` project.
  - `esubdemo` is shared in RStudio Cloud (<https://rstudio.cloud/>)
  - [Project link](https://rstudio.cloud/spaces/183786/join?access_code=FsVLtAUPS9s8uSc38ybNDTr3LYgFWWVq2OQjl8L4).

>>>>

- During the workshop, we will use `esubdemo` project.
  - `esubdemo` is shared in RStudio Cloud (<https://rstudio.cloud/>)
  - You can also clone the `esubdemo` project to your local RStudio.
